### 2017-05-13 paper/evaluation.tex
pass

\noindent\textbf{JUnit.} It is worth mentioning that we used JUnit as
opposed to Maven to run configurations \emph{C*}.  After carefully
verifying library versions for compatibility issues and comparing
results with JUnit's we observed that several of Maven's executions
exposed problems (\eg{} timeouts).  These issues are documented in our
website~\cite{ourwebpage} through Docker containers.  To address those
issues we implemented basic JUnit runner reflecting the effects of
parallel configurations from Maven Surefire.

@@

Our script takes a list
o tests classes to run as an input and outputs the results (\ie,
number of test methods, failures, skips, and elapsed time) for each
parallel configuration. Initially, we use an existing Maven log to
identify the test classes to run, and we use the Maven dependency
plugin~\cite{maven-dep} to build the project's classpath with the
command \CodeIn{mvn dependency:build-classpath}. Once we have the
classpath and the tests to run, we invoke our JUnit runner that runs
the test classes with different parallel configurations at once. For
the sequential execution, we ivonke the default JUnit test runner. For
parallelism within a JVM (\ie, the configurations \SeqClassParMeth{},
\ParClassSeqMeth{}, and \ParClassParMeth{}), we configured the JUnit
runner with ParallelComputer~\cite{junit-parallel} that internally
uses a pool of threads with cache to run test classes and methods. For
the configurations with forked JVMs (\ie, \ForkSeq{} and
\ForkParMeth{}), we have a queue of test classes and a pool of three
threads that ``consumes'' the next test class and spawns a JVM to run
it.  Recall that in our setup (see Section~\ref{sec:setup}), we
limited our kernel to use only three cores and reserved one for
OS-related processes.  To verify that our approach satisfies the
purpose of this experiment, we executed some subjects on Maven and
compared the performance with our artifacts and observed
nonsignificant differences (a fraction of seconds in most cases).
\Comment{ To obtain parallel configurations, we implemented a script
  that takes a subject and a configuration label as inputs (\eg
  \CodeIn{mapdb "c0"}), and the script outputs the modified version of
  the subject with the desired configuration. The workflow consists in
  copying the project directory to a new directory, finding all
  existing build files (\ie, \pomf{} files), and modifying all
  existing Maven Surefire configurations with new values for the
  parameters \CodeIn{parallel}, \CodeIn{forkCount}, and
  \CodeIn{threadCount} using an XPath~\cite{xpath} library to
  manipulate XML documents. For configurations with forked JVMs
  enabled (\ie, \ForkSeq{} and \ForkParMeth{}), we changed the
  \CodeIn{forkCount} with the value \CodeIn{1C} (\ie, one JVM per
  core).  To adjust the pool of threads for parallelism within a JVM,
  we changed the parameter \CodeIn{threadCount} with \Jbc{should we
    consider 2 as it is the number of native threads per core OR 6 as
    it represents 3 Cores * 2 native threads?}.To run the subjects and
  their respective variations (\ie, the modified versions according to
  the parallelism configuration), we used a similar approach as
  described in Figure~\ref{fig:mvn-execution} except that...  } Also,
we used the \CodeIn{timeout} command~\cite{timeout-cmd} in our scripts
to monitor the execution, and we configured the command to dispatch a
\emph{kill} signal if the test execution exceeds a given time
limit. We imposed this time constraint to avoid hanging indefinitely
the experiment execution due to some thread contention that may occur
(\eg, deadlock or livelock).  Finally, we saved each execution log and
stack traces generated outputed from JUnit to collect the execution
time, the number of failing tests, and for reference to analyze and
diagnose outliers in our results.

For
efficiency, we reported the speedup (\ie, $T_{\text{s}} /
T_{\text{p}}$), and for flakiness, we reported the rate of failing
tests (\ie, $\mathit{\%_\text{fail} = failures / tests}$).
Figure~\ref{tab:rq6-table} summarizes the obtained results ordered by
subject's name. Values are reported in average \Fix{LEMBRAR DE MOSTRAR
VALORES DE DESVIO PADRAO!}.

@@

\Jbc{Issues do Maven: (1) Report de contagem de testes, (2) crash de
jvm - maven surefire nao tratava algumas exceptions que aconteciam na
execucao do teste, (3) timeout}

>>>>

It is worth mentioning that we used JUnit as opposed to Maven to run
configurations \emph{C*}.  After carefully verifying library versions
for compatibility issues and comparing results with JUnit's we
observed that several of Maven's executions exposed problems.  For
example, Maven incorrectly counts the number of test cases executed
for some cases where test flakiness are observed.  These issues are
categorized and documented on our website~\cite{ourwebpage} with
Docker containers (for reproduction).  To address those issues we
implemented basic JUnit test runners (one for each \emph{C*}
configuration), reflecting the effects of parallel configurations from
Maven Surefire.  To write those runners we used Maven log files to
identify test classes to run and used the Maven dependency
plugin~\cite{maven-dep} to build the project's classpath with the
command \CodeIn{mvn dependency:build-classpath}. Once we have the
classpath and the tests to run, we invoke our JUnit runner that runs
the test classes with different parallel configurations at once. For
the sequential execution, we ivonke the default JUnit test runner. For
parallelism within a JVM (\ie, the configurations \SeqClassParMeth{},
\ParClassSeqMeth{}, and \ParClassParMeth{}), we configured the JUnit
runner with ParallelComputer~\cite{junit-parallel} that internally
uses a pool of threads with cache to run test classes and methods. For
the configurations with forked JVMs (\ie, \ForkSeq{} and
\ForkParMeth{}), we have a queue of test classes and a pool of three
threads that ``consumes'' the next test class and spawns a JVM to run
it.  Recall that in our setup (see Section~\ref{sec:setup}), we
limited our kernel to use only three cores and reserved one for
OS-related processes.  To verify that our approach satisfies the
purpose of this experiment, we executed some subjects on Maven and
compared the performance with our artifacts and observed
nonsignificant differences (a fraction of seconds in most cases).  To
assure that our experiments terminate (recall tha deadlock or livelock
could occur) we used the \CodeIn{timeout} command~\cite{timeout-cmd}
configured to dispatch a \emph{kill} signal if test execution exceeds
a given time limit. Finally, we saved each execution log and stack
traces generated outputed from JUnit to collect the execution time,
the number of failing tests, and for reference to analyze and diagnose
outliers in our results.

%% \Jbc{Issues do Maven: (1) Report de contagem de testes, (2) crash de
%% jvm - maven surefire nao tratava algumas exceptions que aconteciam na
%% execucao do teste, (3) timeout}

%% The script we implemented to measure time and flakiness takes a list
%% of tests classes to run as input and outputs the results (\ie, number
%% of test methods, failures, skips, and elapsed time) for each parallel
%% configuration.

\Comment{ To obtain parallel configurations, we implemented a script
  that takes a subject and a configuration label as inputs (\eg
  \CodeIn{mapdb "c0"}), and the script outputs the modified version of
  the subject with the desired configuration. The workflow consists in
  copying the project directory to a new directory, finding all
  existing build files (\ie, \pomf{} files), and modifying all
  existing Maven Surefire configurations with new values for the
  parameters \CodeIn{parallel}, \CodeIn{forkCount}, and
  \CodeIn{threadCount} using an XPath~\cite{xpath} library to
  manipulate XML documents. For configurations with forked JVMs
  enabled (\ie, \ForkSeq{} and \ForkParMeth{}), we changed the
  \CodeIn{forkCount} with the value \CodeIn{1C} (\ie, one JVM per
  core).  To adjust the pool of threads for parallelism within a JVM,
  we changed the parameter \CodeIn{threadCount} with \Jbc{should we
    consider 2 as it is the number of native threads per core OR 6 as
    it represents 3 Cores * 2 native threads?}.To run the subjects and
  their respective variations (\ie, the modified versions according to
  the parallelism configuration), we used a similar approach as
  described in Figure~\ref{fig:mvn-execution} except that...  }

%% For efficiency, we reported the speedup (\ie, $T_{\text{s}} /
%% T_{\text{p}}$), and for flakiness, we reported the rate of failing
%% tests (\ie, $\mathit{\%_\text{fail} = failures / tests}$).

@@

Figure~\ref{tab:rq6-table} summarizes the obtained results ordered by
subject's name. Values are reported in average \Fix{LEMBRAR DE MOSTRAR
  VALORES DE DESVIO PADRAO!}.

@@
